### 2024-06-01 2024-5-13/sections/implementation.tex
update description for ComplexCounting benchmark suite and explanation for experiment results

Since the non-register-representable regexes collected from real world are few (5\% of RegCoL and AutomatArk benchmark suites) and simple, there seems no much difference between the performance of $\ostrichrecl$ and its variants ${\rm -NEST}$, ${\rm -COMP}$, ${\rm -FIND}$ in the overall experiment results. Therefore, we consider the ComplexCounting benchmark suite, which contains more complex non-register-representable regexes, to justify the optimizations for non-register-representable regexes. The ComplexCounting benchmark experiment results is shown in Table~\ref{tab:results_heuristic_complex}. We can see that $\ostrichrecl$ solves 82/339/326 more instances and is 1.02/1.92/1.61 times faster than ${\rm -NEST}$/${\rm -COMP}$/${\rm -FIND}$ respectively. From the results, we can conclude that all the optimizations sharply improve the performance of $\ostrichrecl$ on the complex non-register-representable regexes.

>>>>

Since the non-register-representable regexes collected from real world are few (5\% of RegCoL and AutomatArk benchmark suites) and simple, there seems no much difference between the performance of $\ostrichrecl$ and its variants ${\rm -NEST}$, ${\rm -COMP}$, ${\rm -FIND}$ in the overall experiment results. Therefore, we consider the ComplexCounting benchmark suite, which contains more complex non-register-representable regexes, to justify the optimizations for non-register-representable regexes. The ComplexCounting benchmark experiment results is shown in Table~\ref{tab:results_heuristic_complex}. We can see that $\ostrichrecl$ solves 82/339/326 more instances and is 1.02/1.92/1.61 times faster than ${\rm -NEST}$/${\rm -COMP}$/${\rm -FIND}$ respectively. From the results, we can conclude that all the optimizations sharply improve the performance of $\ostrichrecl$ on the non-register-representable regexes.
